---
title: "Hetero Analysis"
author: "Yicheng Shen"
date: "2023/10/30"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, cache = T)
library(mosaic)
library(kableExtra)
library(purrr)
library(gridExtra)
ggplot2::theme_set(ggplot2::theme_bw())
knitr::opts_chunk$set(out.width = "100%", fig.align = 'center')
```


```{r}
res <- read.csv('res/res_binary.csv')   
res2 <- read.csv('res/htelogit_tau50.csv')   
res3 <- read.csv('res/ab_tau50.csv')   

modelname = rep("htelogit_tau50", nrow(res2))
col.group = rep("Bayesian", nrow(res2))
pch.group = rep("HTE model", nrow(res2))

res2 = cbind(res2[, 1:3], modelname, col.group, pch.group, res2[, 4:ncol(res2)])
res2$I.2 = NA


modelname = rep("ablogit_tau50", nrow(res3))
col.group = rep("Bayesian", nrow(res3))
pch.group = rep("HTE model", nrow(res3))

res3 = cbind(res3[, 1:3], modelname, col.group, pch.group, res3[, 4:ncol(res3)])
res3$I.2 = NA

res_all = rbind(res, res2, res3)

result = res_all %>% 
  mutate(modelname = factor(modelname, levels = c("ivfe", "ivre", "ctevaguelogit","ctebeta", "htevaguelogit", "htelogit_tau50", "htebeta", "ablogit", "ablogit_tau50")))
```




```{r, echo = T}
n_distinct(result$MA.id) # number of MAs
nrow(result) # 9 model result per each MA

table((result %>% distinct(MA.id, .keep_all = TRUE))$event)
proportions(table((result %>% distinct(MA.id, .keep_all = TRUE))$event)) * 100
```


```{r}
result = result %>% 
  mutate(Significant_num = 1-as.numeric(0 >= low & 0 <= up)) %>% 
  mutate(Significant = ifelse(Significant_num == "1", "significant", "non-significant"))

result$Significant <- factor(result$Significant, levels = c("significant", "non-significant")) 

missing.MA.id = (result %>% filter(modelname == "htebeta") %>% filter(is.na(est)))$MA.id
result_narm = result %>% filter(! MA.id %in% missing.MA.id)

result_bayesian = result_narm %>% filter(col.group == "Bayesian")
```


# Estimation

```{r, fig.width=12, warning=F}

result$S = ifelse(result$Significant == "significant", T, F)

result %>% filter(event == "common") %>%
  group_by(MA.id) %>%
  mutate(avg_est = mean(est)) %>% 
  arrange(avg_est) %>%
  group_by(modelname) %>%
  mutate(index = row_number()) %>%
  ungroup() %>% 
  filter(index %in% sample(1:22074, 8000, replace = F)) %>%
  ggplot() + 
  geom_point(aes(x = index, y = est, color = Significant), size = 0.1) + 
  geom_ribbon(aes(x = index, ymin = low, ymax = up), alpha = 0.3) + 
  facet_wrap(~modelname) + labs(title = "common event")+ theme(legend.position = "none")


result %>%
  filter(event == "infrequent") %>%
  group_by(MA.id) %>%
  mutate(avg_est = mean(est)) %>% 
  arrange(avg_est) %>%
  group_by(modelname) %>%
  mutate(index = row_number()) %>%
  ungroup() %>% 
  ggplot() + 
  geom_point(aes(x = index, y = est, color = Significant), size = 0.2) + 
  geom_ribbon(aes(x = index, ymin = low, ymax = up), alpha = 0.3) + 
  facet_wrap(~modelname) + 
  labs(title = "infrequent event") + theme(legend.position = "none")


result %>% filter(event == "rare") %>%
  group_by(MA.id) %>%
  mutate(avg_est = mean(est)) %>% 
  arrange(avg_est) %>%
  group_by(modelname) %>%
  mutate(index = row_number()) %>%
  ungroup() %>% 
  ggplot() + 
  geom_point(aes(x = index, y = est, color = Significant), size = 0.2) + 
  geom_ribbon(aes(x = index, ymin = low, ymax = up), alpha = 0.3) + 
  facet_wrap(~modelname) + 
  labs(title = "rare event") + theme(legend.position = "none")


result %>% filter(event == "very rare") %>%
  group_by(MA.id) %>%
  mutate(avg_est = mean(est)) %>% 
  arrange(avg_est) %>%
  group_by(modelname) %>%
  mutate(index = row_number()) %>%
  ungroup() %>% 
  ggplot() + 
  geom_point(aes(x = index, y = est, color = Significant), size = 0.2) + 
  geom_ribbon(aes(x = index, ymin = low, ymax = up), alpha = 0.3) + 
  facet_wrap(~modelname)+ 
  labs(title = "very rare event") + theme(legend.position = "none")
```


# Analysis of heterogeneity estimate

There are three types of model that have $\tau$

1. $\tau$ from `ivre`, `htevaguelogit` and `htelogit_tau50` (log ratios)

```{r, fig.width=15, fig.height=4.5}
result_ivre_tau = result %>% filter(modelname %in% c("ivfe", "ivre")) %>% group_by(MA.id) %>% mutate(diff_est = diff(est)) %>%  filter(modelname == "ivre") %>% ungroup()

result_htelogit_tau50_tau = result %>% filter(modelname %in% c("ctevaguelogit", "htelogit_tau50")) %>% group_by(MA.id) %>% mutate(diff_est = diff(est)) %>%  filter(modelname == "htelogit_tau50") %>% ungroup()

result_htevaguelogit_tau = result %>% filter(modelname %in% c("ctevaguelogit", "htevaguelogit")) %>% group_by(MA.id) %>% mutate(diff_est = diff(est)) %>%  filter(modelname == "htevaguelogit") %>% ungroup()
 
grid.arrange(
result_ivre_tau %>% mutate(plot_mean = mean(diff_est), plot_sd = sd(diff_est)) %>% 
ggplot() + 
  geom_point(data = result_ivre_tau[which(result_ivre_tau$event == "common"),], 
             aes(tau, diff_est, color = event), alpha = 0.5, size = 0.5)+ 
  geom_point(data = result_ivre_tau[which(result_ivre_tau$event == "infrequent"),], 
             aes(tau, diff_est, color = event), alpha = 0.5, size = 0.5)+
  geom_point(data = result_ivre_tau[which(result_ivre_tau$event == "rare"),], 
             aes(tau, diff_est, color = event), alpha = 0.5, size = 0.5)+ 
  geom_point(data = result_ivre_tau[which(result_ivre_tau$event == "very rare"),], 
             aes(tau, diff_est, color = event), alpha = 0.5, size = 0.5) +
  scale_color_manual(values = c("Gray", "Green", "Orange", "Red")) + 
  labs(title = "ivre - ivfe", x = "tau from ivre") + 
  geom_hline(aes(yintercept = plot_mean + 2 * plot_sd), linetype = "dashed", color = "Blue") + 
  geom_hline(aes(yintercept = plot_mean - 2 * plot_sd), linetype = "dashed", color = "Blue")
,
 
result_htevaguelogit_tau %>% mutate(plot_mean = mean(diff_est), plot_sd = sd(diff_est)) %>% 
ggplot() + 
  geom_point(data = result_htevaguelogit_tau[which(result_htevaguelogit_tau$event == "common"),], 
             aes(tau, diff_est, color = event), alpha = 0.5, size = 0.5)+ 
  geom_point(data = result_htevaguelogit_tau[which(result_htevaguelogit_tau$event == "infrequent"),], 
             aes(tau, diff_est, color = event), alpha = 0.5, size = 0.5)+
  geom_point(data = result_htevaguelogit_tau[which(result_htevaguelogit_tau$event == "rare"),], 
             aes(tau, diff_est, color = event), alpha = 0.5, size = 0.5)+ 
  geom_point(data = result_htevaguelogit_tau[which(result_htevaguelogit_tau$event == "very rare"),], 
             aes(tau, diff_est, color = event), alpha = 0.5, size = 0.5) +
  scale_color_manual(values = c("Gray", "Green", "Orange", "Red")) + 
  labs(title = "htevaguelogit - ctevaguelogit", x = "tau from htevaguelogit") + 
  geom_hline(aes(yintercept = plot_mean + 2 * plot_sd), linetype = "dashed", color = "Blue") + 
  geom_hline(aes(yintercept = plot_mean - 2 * plot_sd), linetype = "dashed", color = "Blue") 
,
 
result_htelogit_tau50_tau %>% mutate(plot_mean = mean(diff_est), plot_sd = sd(diff_est)) %>% 
ggplot() + 
  geom_point(data = result_htelogit_tau50_tau[which(result_htelogit_tau50_tau$event == "common"),], 
             aes(tau, diff_est, color = event), alpha = 0.5, size = 0.5)+ 
  geom_point(data = result_htelogit_tau50_tau[which(result_htelogit_tau50_tau$event == "infrequent"),], 
             aes(tau, diff_est, color = event), alpha = 0.5, size = 0.5)+
  geom_point(data = result_htelogit_tau50_tau[which(result_htelogit_tau50_tau$event == "rare"),], 
             aes(tau, diff_est, color = event), alpha = 0.5, size = 0.5)+ 
  geom_point(data = result_htelogit_tau50_tau[which(result_htelogit_tau50_tau$event == "very rare"),], 
             aes(tau, diff_est, color = event), alpha = 0.5, size = 0.5) +
  scale_color_manual(values = c("Gray", "Green", "Orange", "Red")) + 
  labs(title = "htelogit_tau50 - ctevaguelogit", x = "tau from htelogit_tau50") + 
  geom_hline(aes(yintercept = plot_mean + 2 * plot_sd), linetype = "dashed", color = "Blue") + 
  geom_hline(aes(yintercept = plot_mean - 2 * plot_sd), linetype = "dashed", color = "Blue") 
,nrow = 1)
```


```{r, fig.width=12, fig.height=10}
events <- c("common", "infrequent", "rare", "very rare")

result_tau = result %>% 
  filter(modelname %in% c("htevaguelogit", "htelogit_tau50", "ivre")) %>% 
  mutate(num_study = ifelse(num_studies<=20, "medium", "large")) %>% 
  mutate(num_study = ifelse(num_studies<=10, "small", num_study)) %>% 
  mutate(num_study = ifelse(num_studies<=5, "very small", num_study))

plots <- events %>%
  map(~
    result_tau %>% filter(event == .x) %>%
    group_by(modelname) %>% mutate(index = row_number()) %>% ungroup() %>%
    ggplot() +
    geom_point(aes(index, tau, color = num_study), alpha = ifelse(.x %in% c("common", "infrequent"), 0.6, 1), size = ifelse(.x %in% c("common", "infrequent"), 0.3, 0.8)) +
    facet_wrap(~modelname) +
    geom_hline(yintercept = 2) +
    labs(title = .x) 
  )

gridExtra::grid.arrange(grobs = plots, nrow = length(events))
```

2. $\tau_a$ and $\tau_c$ from `ablogit` and `ablogit_tau50` (log odds)

```{r, fig.width=12, fig.height=4}
result_ablogit_tau = result_narm %>% filter(modelname %in% c("ctebeta", "ablogit")) %>% group_by(MA.id) %>% 
  mutate(diff_pa = diff(pa), diff_pc = diff(pc)) %>%  filter(modelname == "ablogit") %>% ungroup()
 
gridExtra::grid.arrange(
result_ablogit_tau %>% mutate(plot_mean = mean(diff_pa), plot_sd = sd(diff_pa)) %>% 
ggplot() + 
  geom_point(data = result_ablogit_tau[which(result_ablogit_tau$event == "common"),], 
             aes(taua, diff_pa, color = event), alpha = 0.5, size = 0.5)+ 
  geom_point(data = result_ablogit_tau[which(result_ablogit_tau$event == "infrequent"),], 
             aes(taua, diff_pa, color = event), alpha = 0.5, size = 0.5)+
  geom_point(data = result_ablogit_tau[which(result_ablogit_tau$event == "rare"),], 
             aes(taua, diff_pa, color = event), alpha = 0.5, size = 0.5)+ 
  geom_point(data = result_ablogit_tau[which(result_ablogit_tau$event == "very rare"),], 
             aes(taua, diff_pa, color = event), alpha = 0.5, size = 0.5) +
  scale_color_manual(values = c("Gray", "Green", "Orange", "Red")) + 
  labs(title = "ablogit - ctebeta", x = "tauc from ablogit") + 
  geom_hline(aes(yintercept = plot_mean + 2 * plot_sd), linetype = "dashed", color = "Blue") + 
  geom_hline(aes(yintercept = plot_mean - 2 * plot_sd), linetype = "dashed", color = "Blue"),

result_ablogit_tau %>% mutate(plot_mean = mean(diff_pc), plot_sd = sd(diff_pc)) %>% 
ggplot() + 
  geom_point(data = result_ablogit_tau[which(result_ablogit_tau$event == "common"),], 
             aes(tauc, diff_pc, color = event), alpha = 0.5, size = 0.5)+ 
  geom_point(data = result_ablogit_tau[which(result_ablogit_tau$event == "infrequent"),], 
             aes(tauc, diff_pc, color = event), alpha = 0.5, size = 0.5)+
  geom_point(data = result_ablogit_tau[which(result_ablogit_tau$event == "rare"),], 
             aes(tauc, diff_pc, color = event), alpha = 0.5, size = 0.5)+ 
  geom_point(data = result_ablogit_tau[which(result_ablogit_tau$event == "very rare"),], 
             aes(tauc, diff_pc, color = event), alpha = 0.5, size = 0.5) +
  scale_color_manual(values = c("Gray", "Green", "Orange", "Red")) + 
  labs(title = "ablogit - ctebeta", x = "tauc from ablogit") + 
  geom_hline(aes(yintercept = plot_mean + 2 * plot_sd), linetype = "dashed", color = "Blue") + 
  geom_hline(aes(yintercept = plot_mean - 2 * plot_sd), linetype = "dashed", color = "Blue"), nrow = 1)




result_ablogit_tau50_tau = result_narm %>% 
  filter(! CDSR.id %in% c("CD002809","CD013438")) %>% 
  filter(modelname %in% c("ctebeta", "ablogit_tau50")) %>% group_by(MA.id) %>% 
  mutate(diff_pa = diff(pa), diff_pc = diff(pc)) %>%  filter(modelname == "ablogit_tau50") %>% ungroup()
 
gridExtra::grid.arrange(
result_ablogit_tau50_tau %>% mutate(plot_mean = mean(diff_pa), plot_sd = sd(diff_pa)) %>% 
ggplot() + 
  geom_point(data = result_ablogit_tau50_tau[which(result_ablogit_tau50_tau$event == "common"),], 
             aes(taua, diff_pa, color = event), alpha = 0.5, size = 0.5)+ 
  geom_point(data = result_ablogit_tau50_tau[which(result_ablogit_tau50_tau$event == "infrequent"),], 
             aes(taua, diff_pa, color = event), alpha = 0.5, size = 0.5)+
  geom_point(data = result_ablogit_tau50_tau[which(result_ablogit_tau50_tau$event == "rare"),], 
             aes(taua, diff_pa, color = event), alpha = 0.5, size = 0.5)+ 
  geom_point(data = result_ablogit_tau50_tau[which(result_ablogit_tau50_tau$event == "very rare"),], 
             aes(taua, diff_pa, color = event), alpha = 0.5, size = 0.5) +
  scale_color_manual(values = c("Gray", "Green", "Orange", "Red")) + 
  labs(title = "ablogit_tau50 - ctebeta", x = "tauc from ablogit_tau50") + 
  geom_hline(aes(yintercept = plot_mean + 2 * plot_sd), linetype = "dashed", color = "Blue") + 
  geom_hline(aes(yintercept = plot_mean - 2 * plot_sd), linetype = "dashed", color = "Blue"),

result_ablogit_tau50_tau %>% mutate(plot_mean = mean(diff_pc), plot_sd = sd(diff_pc)) %>% 
ggplot() + 
  geom_point(data = result_ablogit_tau50_tau[which(result_ablogit_tau50_tau$event == "common"),], 
             aes(tauc, diff_pc, color = event), alpha = 0.5, size = 0.5)+ 
  geom_point(data = result_ablogit_tau50_tau[which(result_ablogit_tau50_tau$event == "infrequent"),], 
             aes(tauc, diff_pc, color = event), alpha = 0.5, size = 0.5)+
  geom_point(data = result_ablogit_tau50_tau[which(result_ablogit_tau50_tau$event == "rare"),], 
             aes(tauc, diff_pc, color = event), alpha = 0.5, size = 0.5)+ 
  geom_point(data = result_ablogit_tau50_tau[which(result_ablogit_tau50_tau$event == "very rare"),], 
             aes(tauc, diff_pc, color = event), alpha = 0.5, size = 0.5) +
  scale_color_manual(values = c("Gray", "Green", "Orange", "Red")) + 
  labs(title = "ablogit_tau50 - ctebeta", x = "tauc from ablogit_tau50") + 
  geom_hline(aes(yintercept = plot_mean + 2 * plot_sd), linetype = "dashed", color = "Blue") + 
  geom_hline(aes(yintercept = plot_mean - 2 * plot_sd), linetype = "dashed", color = "Blue"), nrow = 1)


result_ablogit_tau50_tau = result %>% 
  filter(modelname %in% c("ablogit", "ablogit_tau50"), ! CDSR.id %in% c("CD002809","CD013438")) %>% 
  filter(modelname %in% c("ablogit", "ablogit_tau50")) %>% group_by(MA.id) %>% 
  mutate(diff_pa = diff(pa), diff_pc = diff(pc)) %>%  filter(modelname == "ablogit_tau50") %>% ungroup()
 
gridExtra::grid.arrange(
result_ablogit_tau50_tau %>% mutate(plot_mean = mean(diff_pa), plot_sd = sd(diff_pa)) %>% 
ggplot() + 
  geom_point(data = result_ablogit_tau50_tau[which(result_ablogit_tau50_tau$event == "common"),], 
             aes(taua, diff_pa, color = event), alpha = 0.5, size = 0.5)+ 
  geom_point(data = result_ablogit_tau50_tau[which(result_ablogit_tau50_tau$event == "infrequent"),], 
             aes(taua, diff_pa, color = event), alpha = 0.5, size = 0.5)+
  geom_point(data = result_ablogit_tau50_tau[which(result_ablogit_tau50_tau$event == "rare"),], 
             aes(taua, diff_pa, color = event), alpha = 0.5, size = 0.5)+ 
  geom_point(data = result_ablogit_tau50_tau[which(result_ablogit_tau50_tau$event == "very rare"),], 
             aes(taua, diff_pa, color = event), alpha = 0.5, size = 0.5) +
  scale_color_manual(values = c("Gray", "Green", "Orange", "Red")) + 
  labs(title = "ablogit_tau50 - ablogit", x = "tauc from ablogit_tau50") + 
  geom_hline(aes(yintercept = plot_mean + 2 * plot_sd), linetype = "dashed", color = "Blue") + 
  geom_hline(aes(yintercept = plot_mean - 2 * plot_sd), linetype = "dashed", color = "Blue"),

result_ablogit_tau50_tau %>% mutate(plot_mean = mean(diff_pc), plot_sd = sd(diff_pc)) %>% 
ggplot() + 
  geom_point(data = result_ablogit_tau50_tau[which(result_ablogit_tau50_tau$event == "common"),], 
             aes(tauc, diff_pc, color = event), alpha = 0.5, size = 0.5)+ 
  geom_point(data = result_ablogit_tau50_tau[which(result_ablogit_tau50_tau$event == "infrequent"),], 
             aes(tauc, diff_pc, color = event), alpha = 0.5, size = 0.5)+
  geom_point(data = result_ablogit_tau50_tau[which(result_ablogit_tau50_tau$event == "rare"),], 
             aes(tauc, diff_pc, color = event), alpha = 0.5, size = 0.5)+ 
  geom_point(data = result_ablogit_tau50_tau[which(result_ablogit_tau50_tau$event == "very rare"),], 
             aes(tauc, diff_pc, color = event), alpha = 0.5, size = 0.5) +
  scale_color_manual(values = c("Gray", "Green", "Orange", "Red")) + 
  labs(title = "ablogit_tau50 - ablogit", x = "tauc from ablogit_tau50") + 
  geom_hline(aes(yintercept = plot_mean + 2 * plot_sd), linetype = "dashed", color = "Blue") + 
  geom_hline(aes(yintercept = plot_mean - 2 * plot_sd), linetype = "dashed", color = "Blue"), nrow = 1)
```


```{r, fig.width=12, fig.height=10}
result_tau2 = result %>% 
  filter(modelname %in% c("ablogit", "ablogit_tau50"), ! CDSR.id %in% c("CD002809","CD013438", "CD012859", "CD004278")) %>% 
  mutate(num_study = ifelse(num_studies<=20, "medium", "large")) %>% 
  mutate(num_study = ifelse(num_studies<=10, "small", num_study)) %>% 
  mutate(num_study = ifelse(num_studies<=5, "very small", num_study))


events <- c("common", "infrequent", "rare", "very rare")

plots <- events %>%
  map(~
    result_tau2 %>% filter(event == .x) %>%
    group_by(modelname) %>% mutate(index = row_number()) %>% ungroup() %>%
    ggplot() +
    geom_point(aes(index, taua, color = num_study), alpha = ifelse(.x %in% c("common", "infrequent"), 0.6, 1), size = ifelse(.x %in% c("common", "infrequent"), 0.3, 0.8)) + facet_wrap(~modelname) +
    # geom_hline(yintercept = 2) +
    labs(title = .x) 
  )

gridExtra::grid.arrange(grobs = plots, nrow = length(events))


plots <- events %>%
  map(~
    result_tau2 %>% filter(event == .x) %>%
    group_by(modelname) %>% mutate(index = row_number()) %>% ungroup() %>%
    ggplot() +
    geom_point(aes(index, tauc, color = num_study), alpha = ifelse(.x %in% c("common", "infrequent"), 0.6, 1), size = ifelse(.x %in% c("common", "infrequent"), 0.3, 0.8)) + facet_wrap(~modelname) +
    # geom_hline(yintercept = 2) +
    labs(title = .x) 
  )

gridExtra::grid.arrange(grobs = plots, nrow = length(events))
```

```{r}

```



3. $\tau_a$ and $\tau_c$ from `htebeta` (prob)

```{r, fig.width=12, fig.height=5}
result_htebeta_tau = result_narm %>% filter(modelname %in% c("ctebeta", "htebeta")) %>% group_by(MA.id) %>% 
  mutate(diff_pa = diff(pa), diff_pc = diff(pc)) %>%  filter(modelname == "htebeta") %>% ungroup()
 
gridExtra::grid.arrange(
result_htebeta_tau %>% mutate(plot_mean = mean(diff_pa), plot_sd = sd(diff_pa)) %>% 
ggplot() + 
  geom_point(data = result_htebeta_tau[which(result_htebeta_tau$event == "common"),], 
             aes(taua, diff_pa, color = event), alpha = 0.5, size = 0.5)+ 
  geom_point(data = result_htebeta_tau[which(result_htebeta_tau$event == "infrequent"),], 
             aes(taua, diff_pa, color = event), alpha = 0.5, size = 0.5)+
  geom_point(data = result_htebeta_tau[which(result_htebeta_tau$event == "rare"),], 
             aes(taua, diff_pa, color = event), alpha = 0.5, size = 0.5)+ 
  geom_point(data = result_htebeta_tau[which(result_htebeta_tau$event == "very rare"),], 
             aes(taua, diff_pa, color = event), alpha = 0.5, size = 0.5) +
  scale_color_manual(values = c("Gray", "Green", "Orange", "Red")) + 
  labs(title = "htebeta - ctebeta", x = "taua from htebeta") + 
  geom_hline(aes(yintercept = plot_mean + 2 * plot_sd), linetype = "dashed", color = "Blue") + 
  geom_hline(aes(yintercept = plot_mean - 2 * plot_sd), linetype = "dashed", color = "Blue"),

result_htebeta_tau %>% mutate(plot_mean = mean(diff_pc), plot_sd = sd(diff_pc)) %>% 
ggplot() + 
  geom_point(data = result_htebeta_tau[which(result_htebeta_tau$event == "common"),], 
             aes(tauc, diff_pc, color = event), alpha = 0.5, size = 0.5)+ 
  geom_point(data = result_htebeta_tau[which(result_htebeta_tau$event == "infrequent"),], 
             aes(tauc, diff_pc, color = event), alpha = 0.5, size = 0.5)+
  geom_point(data = result_htebeta_tau[which(result_htebeta_tau$event == "rare"),], 
             aes(tauc, diff_pc, color = event), alpha = 0.5, size = 0.5)+ 
  geom_point(data = result_htebeta_tau[which(result_htebeta_tau$event == "very rare"),], 
             aes(tauc, diff_pc, color = event), alpha = 0.5, size = 0.5) +
  labs(title = "htebeta - ctebeta", x = "tauc from htebeta") + 
  scale_color_manual(values = c("Gray", "Green", "Orange", "Red")) + 
  geom_hline(aes(yintercept = plot_mean + 2 * plot_sd), linetype = "dashed", color = "Blue") + 
  geom_hline(aes(yintercept = plot_mean - 2 * plot_sd), linetype = "dashed", color = "Blue"), nrow = 1)
```


```{r, fig.width=10}
par(mfrow=c(1,2))
plot(density(result_htebeta_tau$taua))
plot(density(result_htebeta_tau$tauc))

grid.arrange(
result_htebeta_tau %>% ggplot() + geom_boxplot(aes(taua, color = event)),
result_htebeta_tau %>% ggplot() + geom_boxplot(aes(tauc, color = event))
)
```

## Correlation of tau

```{r, echo=T}
cor(
  result_bayesian[result_bayesian$modelname == "htelogit_tau50",]$tau,
  result_bayesian[result_bayesian$modelname == "ablogit_tau50",]$taua
  )

cor(
  result_bayesian[result_bayesian$modelname == "htelogit_tau50",]$tau,
  result_bayesian[result_bayesian$modelname == "ablogit_tau50",]$tauc
  )
```


```{r, fig.width=10, out.width="50%"}
result_bayesian_outlier = result_bayesian %>% filter(CDSR.id != "CD002809")
ggplot() + geom_point( aes(
                       result_bayesian_outlier[result_bayesian_outlier$modelname == "htelogit_tau50",]$tau, 
                       result_bayesian_outlier[result_bayesian_outlier$modelname == "ablogit_tau50",]$taua))


ggplot() + geom_point( aes(
                       log(result_bayesian[result_bayesian$modelname == "htelogit_tau50",]$tau), 
                       log(result_bayesian[result_bayesian$modelname == "ablogit_tau50",]$taua)))

ggplot() + geom_point( aes(
                       result_bayesian[result_bayesian$modelname == "htelogit_tau50",]$tau, 
                       result_bayesian[result_bayesian$modelname == "ablogit_tau50",]$tauc))



result_bayesian %>%
  filter(modelname %in% c("htelogit_tau50")) %>%
  mutate(quantile = cut(tau, quantile(tau, probs = c(0, 0.25, 0.5, 0.75, 1), na.rm = T), include.lowest = TRUE)) %>%
  ggplot(aes(x = tau, y = result_bayesian[result_bayesian$modelname == "ablogit_tau50",]$taua, color = quantile)) +
  geom_point(size = 0.4) + theme(legend.position = "none")


result_bayesian %>%
  filter(modelname %in% c("ablogit_tau50")) %>%
  mutate(quantile = cut(taua, quantile(taua, probs = c(0, 0.25, 0.5, 0.75, 1), na.rm = T), include.lowest = TRUE)) %>%
  ggplot(aes(x = result_bayesian[result_bayesian$modelname == "htelogit_tau50",]$tau, y = taua, color = quantile)) +
  geom_point(size = 0.4) + theme(legend.position = "none")

```



```{r, echo=T}
cor(
  result_bayesian[result_bayesian$modelname == "htebeta",]$taua,
  result_bayesian[result_bayesian$modelname == "ablogit_tau50",]$taua
  )

cor(
  result_bayesian[result_bayesian$modelname == "htebeta",]$tauc,
  result_bayesian[result_bayesian$modelname == "ablogit_tau50",]$tauc
  )
```


```{r, fig.width=10, out.width="50%"}
ggplot() + geom_point( aes(
                       result_bayesian[result_bayesian$modelname == "htebeta",]$taua, 
                       result_bayesian[result_bayesian$modelname == "ablogit_tau50",]$taua))

ggplot() + geom_point( aes(
                       result_bayesian[result_bayesian$modelname == "htebeta",]$tauc, 
                       result_bayesian[result_bayesian$modelname == "ablogit_tau50",]$tauc))
```




# Analysis Significance Inference by model 

```{r, fig.width=12, fig.height=8, warning=F, message=F}
result %>% 
  group_by(modelname) %>% summarise(Sig_sum = as.integer(sum(Significant_num, na.rm = T))) %>% mutate(percentage_total = 100 * Sig_sum/table(result$modelname))  %>%
  kbl() %>%
  kable_styling()

result_sigsum = result %>% group_by(MA.id, num_studies, event) %>% summarise(Sig_sum = as.integer(sum(Significant_num, na.rm = T)))

result_sigsum %>% ggplot() + geom_jitter(aes(num_studies, factor(Sig_sum)), alpha = 0.3, height = 0.2) + facet_wrap(~event)
```


```{r, fig.width=12, fig.height=8, warning=F, message=F, echo = T}
table(result_sigsum$Sig_sum)
round(proportions(table(result_sigsum$Sig_sum))*100,3)

table(result_sigsum$event, result_sigsum$Sig_sum)
round(proportions(table(result_sigsum$event, result_sigsum$Sig_sum), margin = 1)*100,2)
```


```{r, fig.width=12, fig.height=8, warning=F, message=F}
result %>% group_by(MA.id) %>% mutate(Sig_sum = as.integer(sum(Significant_num, na.rm = T))) %>% filter(Significant == "significant") %>%
  ggplot(aes(factor(Sig_sum), fill = modelname)) +
  geom_bar(color = "Black") + labs(x = "Number of models with significant results")

result %>% group_by(MA.id) %>% mutate(Sig_sum = as.integer(sum(Significant_num, na.rm = T))) %>% 
  filter(Significant == "significant") %>% 
  ggplot(aes(factor(Sig_sum), fill = modelname)) +
  geom_bar(position = "fill", color = "Black") +
  scale_y_continuous(labels = scales::percent) + labs(x = "Number of models with significant results", y = "proportion") + 
    geom_text(aes(x = factor(Sig_sum), 
                label = scales::percent(after_stat(count / tapply(count, x, sum)[x]), accuracy = 0.01), 
                group = modelname), size = 3, position = position_fill(vjust = .5), stat = "count")  
```








# waic

For best model comparison among seven Bayesian models (exclude ivfe and ivre)

```{r, fig.width=12, fig.height=6}
result_bayesian %>%
  group_by(MA.id) %>%
  mutate(order = rank(waic, ties.method = "min")) %>% 
  ungroup %>% 
  group_by(modelname, order) %>%
  summarize(count = n()) %>%
  mutate(percentage = count / sum(count) * 100) %>%
  ggplot(aes(x = modelname, y = percentage, fill = as.factor(order))) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = paste0(round(percentage, 1), "%"), vjust = -0.5), position = position_dodge(width = 0.9), size = 2) +
  labs(title = "Percentage of Ranking Orders by Model",
       x = "Model",
       y = "Percentage", fill = "waic ranking") +
  scale_fill_manual(values = RColorBrewer::brewer.pal(7, "RdYlBu"))
```

```{r, fig.width=12, fig.height=8}
result_bayesian %>%
  group_by(MA.id) %>%
  mutate(order = rank(waic, ties.method = "min")) %>% 
  ggplot(aes(factor(order), fill = modelname)) +
  geom_bar(position = "fill", color = "Black") +
  geom_text(aes(x = factor(order), 
                label = scales::percent(after_stat(count / tapply(count, x, sum)[x]), accuracy = 0.01), 
                group = modelname), size = 3, position = position_fill(vjust = 0.5), stat = "count") + 
  scale_y_continuous(labels = scales::percent) + 
  labs(x = "waic ranking (1 meaning lowest)", y = "proportion")

```

